---
title: "Exploring Many Variables"
output: html_document
---


Preparation
```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
```

Create a histogram of diamond prices.Facet the histogram by diamond color and use cut to color the histogram bars.

```{r, echo=FALSE}
data(diamonds)
ggplot(aes(x = log10(price)), data = diamonds) +
  facet_wrap( ~color) + 
  geom_histogram(aes(fill = cut)) +
  scale_fill_brewer(type = 'qual')
```

Create a scatterplot of diamond price vs.table and color the points by the cut of the diamond.

```{r, echo=FALSE}
ggplot(aes(x = table, y = price), data = diamonds) +
  geom_point(aes(color = cut)) +
  scale_x_continuous(breaks = seq(50, 80, 2), limits = c(50, 80))
```

Create a scatterplot of diamond price vs. volume (x * y * z) and color the points by
the clarity of diamonds. Use scale on the y-axis to take the log10 of price. You should also
 omit the top 1% of diamond volumes from the plot.

Note: Volume is a very rough approximation of a diamond's actual volume.

```{r, echo=FALSE}
diamonds$volume = with(diamonds, x*y*z)
ggplot(aes(x = volume, y = log10(price)), data = subset(diamonds, volume < quantile(volume, .99))) +
  geom_point(aes(color = clarity))
```

Many interesting variables are derived from two or more others. For example, we might wonder how much of a person's network on a service like Facebook the user actively initiated. Two users with the same degree (or number of friends) might be very different if one initiated most of those connections on the service, while the other initiated very few. So it could be useful to consider this proportion of existing friendships that the user initiated. This might be a good predictor of how active a user is compared with their peers, or other traits, such as personality (i.e., is this person an extrovert?).

Your task is to create a new variable called 'prop_initiated' in the Pseudo-Facebook data set. The variable should contain the proportion of friendships that the user initiated.

```{r, echo=FALSE}
setwd("C:/Users/guochen0706/Downloads")
pf = read.csv('pseudo_facebook.tsv', sep = '\t')
pf$prop_initiated = with(pf, friendships_initiated / friend_count)
```

Create a line graph of the median proportion of 
friendships initiated ('prop_initiated') vs.
tenure and color the line segment by
year_joined.bucket.

Recall, we created year_joined.bucket in Lesson 5
by first creating year_joined from the variable tenure.
Then, we used the cut function on year_joined to create
four bins or cohorts of users.

(2004, 2009]
(2009, 2011]
(2011, 2012]
(2012, 2014]

```{r, echo=FALSE}
pf$year_joined = floor(2014 - pf$tenure / 365)
pf$year_joined.bucket = cut(pf$year_joined, c(2004, 2009, 2011, 2012, 2014))
ggplot(aes(x = tenure, y = prop_initiated), data = subset(pf, !is.na(prop_initiated) & !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), stat = "summary", fun.y = median)
```

Smooth the last plot you created of of prop_initiated vs tenure colored by
year_joined.bucket. You can bin together ranges of tenure or add a smoother to the plot.

```{r, echo=FALSE}
ggplot(aes(x = tenure, y = prop_initiated), data = subset(pf, !is.na(prop_initiated) & !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), stat = "summary", fun.y = median) +
  geom_smooth()
```

For the group with the largest proportion of friendships initiated, what is the group's average(mean) propotion of friendships initiated?

```{r, echo=FALSE}
largest_prop = subset(pf, year_joined > 2012 & !is.na(prop_initiated))
mean(largest_prop$prop_initiated)
```

Create a scatter plot of the price/carat ratio of diamonds. The variable x should be assigned to cut. The points should be colored by diamond color, and the plot should be faceted by clarity.

```{r, echo=FALSE}
ggplot(aes(x = cut, y = price/carat), data = diamonds) +
  facet_wrap(~clarity) +
  geom_jitter(aes(color = color))
```

